---
title: "npsurvSS Overview"
output: html_document
date: "2022-08-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## npsurvSS Overview 

- focus on fixed design 
- implement different type of design for time-to-event data. 

## OOP Definition 

The package define an OOP object as below.  

```
create_arm <- function(size,
                       accr_time,
                       accr_dist = "pieceuni",
                       accr_interval = c(0, accr_time),
                       accr_param = NA,
                       surv_cure = 0,
                       surv_interval = c(0, Inf),
                       surv_shape=1,
                       surv_scale,
                       loss_shape=1,
                       loss_scale,
                       follow_time = Inf,
                       total_time = Inf) 
```

It is an OOP object contain all components for a single arm. 
The design provide flexibility to extend by 

- define different arms for each stratum, each can have complete freedom. 
  - e.g. define a stratum that is added/droped in the middle of a trial. 
- potential extend to adaptive design for quick simulation based evaluation.
  - e.g a comparision between group sequential design and other adaptive design with limited budget. 

## Distribution Definition

The package define a set of distribtion to streamline mathmatical implementation.


For each distribution, we can implement `p`, `q`, `d`, `r`, `h`. 
This is the same strategy as in `npsurvSS`, where we have 

- accumulation distribution `paccr`, `qaccr`, `daccr`, `raccr`, `haccr`.
- event distribtion `psurv`, `qsurv`, `dsurv`, `rsurv`, `hsurv`. 
- censoring distribution `ploss`, `qloss`, `dloss`, `rloss`, `hloss`.

## Simulation one Arm 

With the OOP object and distribution functions `rsurv`, `raccr` and `rloss`, 
the data simulation step is simply simulate data from
a `arm` object using `rsurv`, `raccr` and `rloss`. 

With a combination of different arm, and different analysis approach, 
we have full flexibility to evaluate operational characteritics 
for complicated group sequential design and adaptive design. 

## Probability of Event in Calendar Time  

For each Arm, the probability of event at different time point is independent of study design 
given the `arm` OOP object. 

The key is to define `p`, `q`, `d` and `h` of counting process by 
distributions defined previously. 

Here is the definition in `npsurvSS`. 

```{r, eval = FALSE}
dens_event <- function(arm, teval) {
  dsurv(teval, arm) *
    ploss(teval, arm, lower.tail=F) *
    paccr(pmin(arm$accr_time, arm$total_time-teval), arm)
}
```

## Probability at Risk in Calendar Time 

For each Arm, the probability at risk at different time point is independent of study design
given the `arm` OOP object.

The key is to define `p`, `q`, `d` and `h` of counting process by 
distributions defined previously. 

Here is the definition in `npsurvSS`. 

```{r, eval = FALSE}
prob_risk <- function(arm, teval) {
  psurv(teval, arm, lower.tail=F) *
    ploss(teval, arm, lower.tail=F) *
    paccr(pmin(arm$accr_time, arm$total_time-teval), arm)
}
```


## Power and Sample Size 

For fixed design, the sample size can be obtained 
after we can derive the effect size based on the information we have above. 

The details is in Godwin's paper or our training materials. 



